The SMT Competition 2015--2018

### 2019-08-27 2018/report/SMT-COMP.tex
Minor

%\usepackage{showframe}   % debug

@@

For incremental benchmarks, the situation is different: an incremental
benchmark is ineligible for the \apptrack if its first {\tt
  check-sat} command has unknown status.  Otherwise, the prefix of the
benchmark that only contains {\tt check-sat} commands with known
status is eligible.  The main reason for this difference is that the
competition tools for the \apptrack (in particular, the trace
executor) have not been adapted yet to support {\tt check-sat}
commands with unknown status. Even though the trace executor has now been modified, we cannot check what impact this may have had on previous results without rerunning all tracks as the trace executor drives the solver.

>>>>

@@

For incremental benchmarks, the situation is different: an incremental
benchmark is ineligible for the \apptrack if its first {\tt
  check-sat} command has unknown status.  Otherwise, the prefix of the
benchmark that only contains {\tt check-sat} commands with known
status is eligible.  The main reason for this difference is that the
competition tools for the \apptrack (in particular, the trace
executor) had not been adapted yet to support {\tt check-sat}
commands with unknown status. Even though the trace executor has now been modified, we cannot check what impact this may have had on previous results without rerunning the \apptrack as the trace executor drives the solver.
